Analyzing microtomography data with Python and the scikit-image library

### 2016-11-01 answer_to_referees.txt

* The discussion about skimage functionality (fig 5) was very fast and
  felt a bit disjointed.

Image processing is a very broad field, and scikit-image provides a large
variety of processing operations. Therefore, we chose to illustrate only
a few capabilities of scikit-image, since a lengthy list would bore the
reader, while not being very instructive. Nevertheless, the choice of
these operations, and the link between them, might have been better
explained. We now explain why denoising, object detection and
measurements are important for processing microtomography images "In the
following, we briefly illustrate how scikit-image can be used for some
typical image processing tasks encountered when analyzing tomographic
images: denoising, mid-range feature detection, segmentation and
measurement of region properties. For the sake of brevity, other tasks
such as contrast manipulation or geometric transformations are not
described here; the interested reader is referred to the documentation
of scikit-image.", "Denoising data is often the first step of an image
processing workflow", "Detecting the presence of objects or extracting
pixels corresponding to objects (a task known as segmentation) is an
important task of image analysis for medical or materials science
applications.". We have also improved transitions between paragraphs.

* Given the recent discussions of system package managers vs conda/EPD vs
  pip (ex
http://www.curiousefficiency.org/posts/2016/09/python-packaging-ecosystem.html)
I suggest re-wording the getting started section.

Python packaging is a broad topic, that goes well beyond the scope of our
paper. As explained in the blog post cited by the referee, different
solutions each have their pros and cons. The purpose of the "getting
started" section is mostly to give some pointers to the readers, rather
than engaging in a discussion on packaging. For the sake of completeness,
we now mention conda as a command-line tool for Anaconda (the most common
use of conda).

@@

We increased the font size in Figures 3 and 6 (modifying the layout of
Figure 6 to this end).

- Fig 5: for the non-synthetic data sets: could one perhaps state where the data
was taken, i.e. in the acknowledgement? Scale                                   
bars are also missing.

Scale bars were actually omitted on purpose, since Fig. 5 is a very busy
figure, and its interest lies mostly in the application of image
processing operations, not in the original samples and images
themselves.

We have acknowledged the origin of the neurons image of Fig. 5 (b),
which was the only non-synthetic image for which the origin was missing.

### 2016-11-01 skimage_tomo.tex
Final minor modifications before resubmission.

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
and its distribution Fiji \citep{Schindelin2012} is a popular
general-purpose tool for 2-D and 3-D images, thanks to its intuitive
menus and graphical tools, and the wealth of plugins contributed by a
vivid community \citep{Schindelin2015}. Software specialized in analyzing
synchrotron data are available as well, such as XRDUA~\citep{xrdua} for
diffraction images obtained in powder diffraction analysis, or  For 3-D
images, commercial tools such as Avizo 3D software (TM), or
ToolIP/MaviKit~\citep{mavi} are appreciated
for an intuitive graphical pipeline and advanced 3D visualization. Some
synchrotrons have even developed their own tools for volume processing,
such as Pore3D~\citep{Brun2010} at the Elettra facility. Alternatively,
the use of a programming language gives finer control, better
reproducibility, and more complex analysis possibilities, provided
classical processing algorithms can be called from libraries -- thereby
limiting the complexity of the programming task and the risk of bugs.
Matlab (TM) and its image processing toolbox are popular in the academic
community of computer vision and image processing. The Python language is
widely used in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers \citep{pytango, Sugandhi2016, nsls-ii}, to access raw data
of X-ray detectors \citep{Knudsen2013}, to reconstruct tomography volumes
from radiographs \citep{Gursoy2014, Mirone2014}, and in data processing
packages for macromolecular cristallography \citep{Adams2010}, azimuthal
integration of diffraction data \citep{Ashiotis2015}, or fluorescence
analysis \citep{pymca, Sole2007}.

@@

In this section, we provide a short overview of the typical use patterns of
\texttt{scikit-image}, illutrated by short snippets of code. Since
Python is a programming language, the user interacts with data objects and
images through code, which is either entered and executed in an interactive
interpreter, or written in text files (so-called scripts) that are executed.

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.95\textwidth]{figure_gallery}}
\caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
 The gallery of examples consists of an array of thumbnails (left), which link to example webpages, each centerered on a specific image processing task. Each webpage includes Python code generating a figure, the figure itself, and a short tutorial explaining the image processing operations and the code. \label{fig:gallery}}
\end{figure*}

>>>>

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
and its distribution Fiji \citep{Schindelin2012} is a popular
general-purpose tool for 2-D and 3-D images, thanks to its intuitive
menus and graphical tools, and the wealth of plugins contributed by a
vivid community \citep{Schindelin2015}. Software specialized in analyzing
synchrotron data are available as well, such as XRDUA~\citep{xrdua} for
diffraction images obtained in powder diffraction analysis, or  For 3-D
images, commercial tools such as Avizo 3D software (TM), or
ToolIP/MAVIkit~\citep{mavi} are appreciated
for an intuitive graphical pipeline and advanced 3D visualization. Some
synchrotrons have even developed their own tools for volume processing,
such as Pore3D~\citep{Brun2010} at the Elettra facility. Alternatively,
the use of a programming language gives finer control, better
reproducibility, and more complex analysis possibilities, provided
classical processing algorithms can be called from libraries -- thereby
limiting the complexity of the programming task and the risk of bugs.
Matlab (TM) and its image processing toolbox are popular in the academic
community of computer vision and image processing. The Python language is
widely used in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers \citep{pytango, Sugandhi2016, nsls-ii}, to access raw data
of X-ray detectors \citep{Knudsen2013}, to reconstruct tomography volumes
from radiographs \citep{Gursoy2014, Mirone2014}, and in data processing
packages for macromolecular cristallography \citep{Adams2010}, azimuthal
integration of diffraction data \citep{Ashiotis2015}, or fluorescence
analysis \citep{pymca, Sole2007}.

@@

In this section, we provide a short overview of the typical use patterns of
\texttt{scikit-image}, illustrated by short snippets of code. Since
Python is a programming language, the user interacts with data objects and
images through code, which is either entered and executed in an interactive
interpreter, or written in text files (so-called scripts) that are executed.

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.95\textwidth]{figure_gallery}}
\caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
 The gallery of examples consists of an array of thumbnails (left), which link to example webpages, each centered on a specific image processing task. Each webpage includes Python code generating a figure, the figure itself, and a short tutorial explaining the image processing operations and the code. \label{fig:gallery}}
\end{figure*}
